---
caption: 07 ProblemSet
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1
### a)
First all the files are read in and parsed so that each row contains an observation and each column a variable. For every file the corresponding Season and episode were appended.

```{r tidyText, echo=FALSE, warning=FALSE, message=FALSE}
library(magrittr)
library(dplyr)
library(tidytext)

tidyText <- NULL
for (i in 1:6) {
  season <- paste0("S0",i)
  for (j in 1:10) {
    episode <- ifelse(j<10,paste0("E0",j), paste0("E",j))
    seaEp <- paste0(season, episode)
    
    file <- scan(seaEp, what = "character", quiet = T, quote = "")
    words <- data.frame(file)
    colnames(words) <- c("word")
    words %>%
      filter(!grepl("[0-9]{2,}[:, ]|[0-9]{3}", word))%>%
      filter(!grepl("-->",word))%>%
      filter(!grepl("^[0-9]+", word))%>%
      filter(!grepl("-",word))%>%
      filter(!grepl("[A-Z]{2,}",word))%>%
      mutate(word=gsub("\\?","",word))%>%
      mutate(word=gsub("\\.","",word))%>%
      mutate(word=gsub("^<i>","",word))%>%
      mutate(word=gsub("</i>$","",word))%>%
      filter(!grepl(">",word))%>%
      filter(!grepl("<",word))%>%
      filter(!grepl("&",word))%>%
      filter(!grepl("_",word))%>%
      mutate(word=gsub("\\,","",word))-> words
    
    words <- cbind(words, season = rep(season,nrow(words)), episode = rep(episode,nrow(words)))
    
    tidyText <- rbind(tidyText, words)
  }
}
head(tidyText,10)
```

Now the words will be examined further. First all words are being count and without stop word removal and after with removed stop words.

```{r CountwStopWords}
tidyText%>%
  count(word,sort=TRUE)
```

Here is the word count with removed stop words

```{r countnoStopWords, message=FALSE}
tidyText%>%
  anti_join(stop_words)%>%
  count(word,sort=TRUE)
```

As you can see, not all stop words have been removed. All frequent words are in upper case. Therefore it is further necessary to convert all words from upper to lowercase. Otherwise the stop words will not be removed. Which is done in the following code

```{r lowerCase, message=FALSE}
tidyText%>%
  mutate(word = tolower(word))%>%
  anti_join(stop_words)-> tidyText

tidyText%>%
  count(word,sort=TRUE)


```

Now we want to know what the 10 most frequent words for each episode are.
```{r freqWord, echo=FALSE, message=FALSE, results='asis'}

for (i in 1:6) {
    sea <- paste0("S0",i)
    tidyText%>%
      filter(grepl(sea, season))%>%
      count(word,sort=TRUE)%>%
      head(.,10)%>%
      as.data.frame(.)%>%
      assign(sea,.,inherits = TRUE)
}
knitr::kable(S01, caption = "S01", align = 'l')
knitr::kable(S02, caption = "S02", align = 'l')
knitr::kable(S03, caption = "S03", align = 'l')
knitr::kable(S04, caption = "S04", align = 'l')
knitr::kable(S05, caption = "S05", align = 'l')
knitr::kable(S06, caption = "S06", align = 'l')
```

### b)

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
